On Secure Delegation of SampBQP with a Classical Client

### 2019-11-24 qpip.tex
Fix typo

	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
			\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
			\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies in sequence and without replacement
			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
			\If{over $(\frac{1}{2}-2\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a fresh copy from the prover
				\If{Measured $t\geq T$}
					\State Measure and output the other registers
				\EndIf
			\EndFor
			\State Reject
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-2\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}. By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.

>>>>

	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
			\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
			\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies in sequence and without replacement
			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
			\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a fresh copy from the prover
				\If{Measured $t\geq T$}
					\State Measure and output the other registers
				\EndIf
			\EndFor
			\State Reject
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}. By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
